---
title: "Minimal best linear predictor example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Minimal best linear predictor example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blpopt)
library(grf)
library(ggplot2)

theme_set(theme_minimal())
```

## Create simulated data

```{r, data-generation}
n <- 2000
p <- 20
X <- matrix(rnorm(n * p), n, p)

# CATE varies along one dim only.
tau_ex <- function(x) {
  1 / (1 + exp(-x))
}
TAU <- tau_ex(X[, 3])

# Propensity  and Outcome vary along 2 and 5 dimensions only.
W <- rbinom(n, 1, 1 / (1 + exp(-X[, 1] - X[, 2])))
Y <- pmax(X[, 2] + X[, 3], 0) + rowMeans(X[, 4:6]) / 2 + W * TAU + rnorm(n)
```

## Estimate causal forest and fit Conditional Average Treatment Effect
Best Linear Predictor (CATE-BLP)

```{r, estimate}
cf <- causal_forest(X, Y, W)
blp <- cate_blp(cf, X[, 3])
```

```{r, summary}
summary(blp)
```

## Extract predictions

```{r, predictions}
predicted <- predict(blp)
```


## Visualize approximations and compare to true CATE

In the following plot:

- The red line shows the true conditional average treatment effect ($\tau$).

- Black points are the estimated best linear predictions of the CATE

```{r, visually-compare}
ggplot(predicted, aes(x = A, y = predicted)) +
  xlim(c(min(predicted$A), max(predicted$A))) +
  geom_function(fun = tau_ex, col = "red") +
  geom_point(size = 1, alpha = 0.4)
```

## Estimate the impact of using approximately optimal targeting to assign treatment

We can get a sense of the value of using approximately optimal targeting
over no targeting using bootstraped predictions of the incremental effect
for the treated population:

```{r}
total_pred <- cate_blp_bootstrap(blp, iterations = 1000)

total_pred$difference_blp <- total_pred$predicted_optimal - total_pred$predicted_totals

median(total_pred$difference_blp)
```

```{r}
ggplot(total_pred, aes(difference_blp)) +
    geom_density(alpha = 0.7) +
    xlab("\nPredicted Incremental Profit") +
    ggtitle("Bootstraped Predicted Incremental Profit of using\nApproximately Optimal vs 'Treat All' targeting\nfor a population with characteristics A")
```

