---
title: "Minimal best linear predictor example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Minimal best linear predictor example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blpopt)
library(grf)
library(ggplot2)
```

## Create simulated data

```{r, data-generation}
n <- 2000
p <- 20
X <- matrix(rnorm(n * p), n, p)

# CATE varies along one dim only.
tau_ex <- function(x){1 / (1 + exp(-x))} 
TAU <- tau_ex(X[,3])

# Propensity  and Outcome vary along 2 and 5 dimensions only.
W <- rbinom(n, 1, 1 / (1 + exp(-X[, 1] - X[, 2]))) 
Y <- pmax(X[, 2] + X[, 3], 0) + rowMeans(X[, 4:6]) / 2 + W * TAU + rnorm(n)
```

## Estimate causal forest and fit Conditional Average Treatment Effect
Best Linear Predictor (CATE-BLP)

```{r, estimate}
cf <- causal_forest(X,Y,W)
blp <- cate_blp(cf,X[,3])
```

## Extract predictions (TO-UPDATE with predict method)

```{r, predictions}
preds <- cbind(1, X[,3]) %*% blp[,1] 
plt_df <- data.frame(x=X[,3],y=preds)
```


## Visualize approximations and compare to true CATE

In the following plot:

- The red line shows the true conditional average treatment effect ($\tau$).

- Black points are the estimated best linear predictions of the CATE

```{r, visually-compare}
ggplot(plt_df,aes(x=x,y=y)) +
  xlim(c(min(plt_df$x), max(plt_df$x))) +
  geom_function(fun = tau_ex,col="red")  + 
  geom_point(size = 1, alpha = 0.4) +
  theme_minimal()
```
